Openness and computational reproducibility in plant pathology: where do we stand and a way forward

### 2022-07-08 analysis/paper/paper.Rmd
quote 'yrep' and 'y' in caption describing figure 1
Clarify scoring and data cleaning

@@

@@

```{r posteriors, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Posterior distribution visualizations for each of six models fitted to scoring data that were used to evaluate factors on reproducibility of 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals. The journal title was tested for an effect on code availability (A) and data availability (B), the year of publication was tested for an effect on code availability (C) and data availability (D), and five-year impact factor of journal was tested for effect on code availability (E) and data availability (F). Where yrep indicate 50 random draws for model predictions and y are the observed values. Model fitnesses were found to be good for all models.", cache=FALSE, fig.env='figure'}

>>>>

In cases where partial computational materials or data were made available, the score was assigned the lowest score reflecting the completeness of the availability, all or nothing.
That is, in cases where some data such as sequences were deposited in a database, *e.g.*, GenBank, but other data that was collected and used were not made available, the score assigned was '0'.

@@

The criteria scores were checked for inconsistencies using the evaluators' comments in the spreadsheet and based on the software used.
In some cases these comments were used to adjust the criteria score to align with the scoring definitions.
This was not possible in all cases but only in cases where the evaluator had left comments that could be checked and acted upon.
For example, a reviewer noted that all data were deposited in GenBank but the data score was '0', this was changed to '3' to align with the definition.
Or in other cases, some software packages used were Excel add-ins but Excel was not recorded as being used; Excel was added to the list of software used to rectify this.

@@

```{r posteriors, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Posterior distribution visualizations for each of six models fitted to scoring data that were used to evaluate factors on reproducibility of 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals. The journal title was tested for an effect on code availability (A) and data availability (B), the year of publication was tested for an effect on code availability (C) and data availability (D), and five-year impact factor of journal was tested for effect on code availability (E) and data availability (F). Where 'yrep' indicate 50 random draws for model predictions and 'y' are the observed values. Model fitnesses were found to be good for all models.", cache=FALSE, fig.env='figure'}
